---
title: "R"
output:
  html_document: default
---

download package ggplot2
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("ggplot2")
library(ggplot2)
```

import the data("iris")
```{r}
data("iris")
```

make a scatter plot with x-axis: Sepal.Length and y-axis: Sepal.Width, and the species should be shown in different colors
```{r}
print( p <- ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) + geom_point() )
```

add regression line for the previous plot with the whole dataset (regardless of the species)
```{r}
p + geom_smooth(method="lm", se=FALSE, color="black") # reusing above plot
```

calculate the Pearson correlation for this plot
```{r}
cor.test(iris$Sepal.Length, iris$Sepal.Width, method="pearson")
```

make the boxplot for Petal.Width with 3 species separately in the x-axis in different colors
```{r}
ggplot(iris, aes(x=Species, y=Petal.Width, fill=Species)) + geom_boxplot()
```

make the histogram for Petal.Width with 3 species separately in x-axis in different colors
```{r}
ggplot(iris, aes(x=Petal.Width, fill=Species)) + geom_histogram()
```

run the t-test of Petal.Width between setosa and virginica, and give the conclusion if the width is a statistically significant difference between 2 species

```{r}
t_test <- t.test(
  subset(iris, Species == "setosa")$Petal.Width,
  subset(iris, Species == "virginica")$Petal.Width,
)
cat("Conclusion: The petal width between setosa and virginica is statistically", if(t_test$p.value > 0.05) "not", "significant.\n")
```
